Results

### 2018-08-01 4-results-simus.Rmd
new figures

```{r, fig.asp = 1, out.width = "90%"}
results4 %>%
  filter(method %in% c("logit-simple", "PRS-max")) %>%
  mutate(method = c_method_r2(method, thr.r2)) %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  barplot_causal_all()

>>>>

```{r}
results4 %>%
  filter(method %in% c("logit-simple", "PRS-max")) %>%
  mutate(method = c_method_r2(method, thr.r2)) %>%
  group_by_at(c(vars(starts_with("par")), "method")) %>%
  summarise(AUC_mean = mean(AUC), AUC_boot = boot(AUC), N = n()) %>%
  barplot_causal_all()
